---
title: "PowerAnalysis-LabelConcept"
author: "Bria Long"
date: "3/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(BayesFactor)
```

## Extract effect sizes from meta-analysis for conditions and age ranges of interest

```{r}
meta=as.tibble(read.csv('Label advantage in concept learning.csv')) 

effectSizes_All<- meta %>%
  filter(audio_condition %in% c("noun","silence", "non-linguistic sound")) %>%
  group_by(audio_condition) %>%
  summarize(meanEffect = mean(g_calc), sdEffect = sd(d_calc))%>%
  data.frame

effectSizes_Targeted<- meta %>%
  filter(audio_condition %in% c("noun","silence", "non-linguistic sound")) %>%
  mutate(mean_age_months > 12) %>%
  filter(response_mode=="eye-tracking") %>%
  group_by(audio_condition) %>%
  summarize(meanEffect = mean(g_calc), sdEffect = sd(d_calc))
```
To gain clarity on this complex literature, we conducted a systematic meta-analysis of this literature, including `r length(meta$study_ID)` conditions from `r length(unique(meta$study_ID))` papers and `r sum(meta$n)` infants, finding an overall effect size of Hedges’ g = `r round(mean(meta$g_calc),2)`. These effect sizes differed considerably based on the auditory stimuli that infant's heard: nouns elicited consistency greater novelty preferences than non-linguistic tones (noun, Hedges' g M = `r round(effectSizes_All$meanEffect[2],2)`, SD = `r round(effectSizes_All$sdEffect[2],2)`; tones, Hedges' g M = `r round(effectSizes_All$meanEffect[1],2)`, SD = `r round(effectSizes_All$sdEffect[1],2)`); however, categories learned during silent conditions also generated novelty preferences (silence, Hedges' g M = `r round(effectSizes_All$meanEffect[3],2)`, SD = `r round(effectSizes_All$sdEffect[3],2)`.

```{r}
knitr::kable(effectSizes_All, digits = 2)
```


## Simulate s
```{r}
# Simulation-based bayesian power analysis with prior over ES
ES_mean_tones <- effectSizes_Targeted$meanEffect[1]
ES_sd_tones <- effectSizes_Targeted$sdEffect[1]

ES_mean_labels <- effectSizes_Targeted$meanEffect[2]
ES_sd_labels <- effectSizes_Targeted$sdEffect[2]

n_sims <- 500
ns <- c(20,40,60,70,80,100)

sims <- as.tibble(expand.grid(sim = 1:n_sims, 
                              n = ns)) %>%
  mutate(idx = 1:n()) %>%
  split(.$idx) %>%
  map_df(function (x) {
    mu_es_labels <- rnorm(n = 1, mean = ES_mean_labels, sd = ES_sd_labels)
    mu_es_tones <- rnorm(n = 1, mean = ES_mean_tones, sd = ES_sd_tones)
    es_diff_sim <- mu_es_labels - mu_es_tones # output simulated diff in effect size - labels vs. tones
    
    d1 <- rnorm(n = x$n, mean = mu_es_labels)
    d2 <- rnorm(n = x$n, mean = mu_es_tones)
    x$p <- t.test(d1, d2)$p.value
    x$bf <- extractBF(BayesFactor::ttestBF(d1, d2))$bf
    x$es_diff_sim <- es_diff_sim
    return(x)
  })

sims %>%
  group_by(n) %>%
  summarise(power = mean(p < .05), 
            meanbf = mean(bf > 6) )


```

