---
title: "PowerAnalysis-LabelConcept"
author: "Bria Long"
date: "3/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(BayesFactor)
library(BFDA)
```

## Extract effect sizes from meta-analysis for conditions and age ranges of interest
```{r}
meta=as.tibble(read.csv('Label advantage in concept learning.csv')) 

# reported in abstract, across all conditions and ages
effectSizes_All<- meta %>%
  filter(audio_condition %in% c("noun","silence", "non-linguistic sound")) %>%
  group_by(audio_condition) %>%
  summarize(meanEffect = mean(g_calc), sdEffect = sd(d_calc), countStudies = length(g_calc))

# used for power analysis -- target
effectSizes_Targeted<- meta %>%
  filter(audio_condition %in% c("noun","silence", "non-linguistic sound")) %>%
  filter(mean_age_months >= 11) %>%
  filter(mean_age_months <= 17) %>%
  filter(response_mode=="eye-tracking") %>%
  group_by(audio_condition) %>%
  summarize(meanEffect_Targeted = mean(g_calc),sdEffect_Targeted = sd(g_calc), countStudies = length(g_calc))
```
To gain clarity on this complex literature, we conducted a systematic meta-analysis of this literature, including `r length(meta$study_ID)` conditions from `r length(unique(meta$study_ID))` papers and `r sum(meta$n)` infants, finding an overall effect size of Hedges’ g = `r round(mean(meta$g_calc),2)`. These effect sizes differed considerably based on the auditory stimuli that infant's heard: nouns elicited consistency greater novelty preferences than non-linguistic tones (noun, Hedges' g M = `r round(effectSizes_All$meanEffect[2],2)`, SD = `r round(effectSizes_All$sdEffect[2],2)`; tones, Hedges' g M = `r round(effectSizes_All$meanEffect[1],2)`, SD = `r round(effectSizes_All$sdEffect[1],2)`); however, categories learned during silent conditions also generated novelty preferences (silence, Hedges' g M = `r round(effectSizes_All$meanEffect[3],2)`, SD = `r round(effectSizes_All$sdEffect[3],2)`.

```{r}
knitr::kable(effectSizes_All, digits = 2)
knitr::kable(effectSizes_Targeted, digits = 2)
```



```{r}
## parameters for both simulations and analyses
boundaryBF = 10
n.min = 20
n.max = 50
stepsize = 5

## H1: Difference between labels and tones is as predicted by meta-analysis
LabelsVTones = effectSizes_Targeted$meanEffect_Targeted[2]-effectSizes_Targeted$meanEffect_Targeted[1]
s1 <- BFDA.sim(expected.ES=LabelsVTones, n.min=n.min, stepsize=stepsize, n.max=n.max, type="t.between", design="sequential", r=sqrt(2)/2, alternative="directional", cores=4, boundary=boundaryBF)
a1 <- BFDA.analyze(s1, design="sequential", n.min=n.min, boundary=boundaryBF)
plot(s1)

## Null hypothesis: no difference between labels and tones
s0 <- BFDA.sim(expected.ES=0, n.min=n.min, stepsize=stepsize, n.max=n.max, type="t.between", design="sequential", r=sqrt(2)/2, alternative="directional", cores=4,boundary=boundaryBF)
a0 <- BFDA.analyze(s0, design="sequential", n.min=n.min, boundary=boundaryBF)
plot(s0)


```

